\section{Diversity of Dwarf Diffusion}

% 
There are only so many conclusions we can draw about the diversity of dwarf sizes with the given data. The data from \cite{mcconnachieOBSERVEDPROPERTIESDWARF2012} spans the range of $10^2$ to $10^9$ solar masses, with many of the galaxies observed being smaller than $3 \cdot 10^6$. The FIREbox data, however, only covers galaxies greater than $3 \cdot 10^6$. For this reason and others, the lines of best fit defined by $\ln(a)$ and $\gamma$ (see equation \ref{equ:linear-rel}) for each dataset do not perfectly line up. %TODO: \ref{fig}
The diffuseness parameter $\beta$ is defined relative to the line of best fit for a dataset. It is therefore important to note that the $\beta$ for individual galaxies across datasets have no meaningful comparison. However, we may still compare the overall diversity of the diffuseness. For FIREbox we have $\sigma_\beta = 0.28$, and for \cite{mcconnachieOBSERVEDPROPERTIESDWARF2012} we have a diversity of $\sigma_\beta = 0.66$, over twice as large. The simulated galaxies in FIREbox therefore follow a much stricter size-mass relationship than is expected from real-world observation.

This discrepancy is an example of the diversity of dwarf sizes tension, and \cite{salesBaryonicSolutionsChallenges2022} has shown that it applies to many zoom-in simulations as well. FIREbox has a larger volume and contains more galaxies than those simulations, and is the first of its size to be detailed enough to include dwarf galaxies. It is therefore an important finding that the tension is not resolved in FIREbox, because that is evidence that the tension is \emph{not} caused by a constraint in simulation volume.

\section{Proximity to Nearest Neighbor}