% Here we have your executive summary.

Cosmological simulations are an important part of our understanding of the universe. They allow us to test our theories about cosmology by seeing if the simulated behavior created by those theories aligns with the real world. The FIREbox galaxy simulation uses the theory of \textbf{\lcdm}, the current most popular model of dark matter and dark energy. It models a box of over 1700 galaxies from their initial creation all the way through the present day. This present day state can be compared to real world galaxies to determine what simulated characteristics align with the real ones.

When a certain characteristic of the simulation does not line up with observational data, it is called a \textbf{tension}. One such tension is that of the diversity of low-mass galaxy sizes. The low-mass galaxies near the Milky Way (known as the \textbf{Local Group}) have much variation in radius compared to their mass. In other words, they range from very compact to very diffuse. However, most historical \emph{simulated} galaxies have a much stricter size-mass ratio. This discrepancy is the driving motivation for this thesis.

To examine this tension further, I compare the diffuseness of galaxies from the FIREbox cosmological simulation with other galactic properties. I define the \textbf{diffuseness} ($\beta$) of a galaxy to be how much it deviates from the expected size-mass ratio. This parameter is useful for our study because, by design, it is independent of mass for low-mass galaxies. We are therefore free to correlate it with other parameters.

One theory for the variation in diffuseness is tidal interactions. A tidal interaction occurs when a galaxy comes in close contact with another, and its outer layers get stretched by the other's gravity. Tidal forces therefore could cause greater diffuseness. Satellite galaxies are ones that orbit other galaxies. By examining the relationship between a satellite and its host galaxy, one may find the potential effects of tidal forces on galaxy diffuseness. I compared the diffuseness of satellite galaxies with the distance to their hosts: both in the present and when they was at their \emph{minimum} distance. I found that when one expresses the distance as a fraction of the host galaxy's virial radius, there is a correlation. Specifically, the closer a satellite gets to its host, the more diffuse it becomes.